
\section{{\textcolor{mainHeading}{Experience}}}
    \resumeSubHeadingListStart
    % Makerble
    \resumeSubheadingConditional
      {\textbf{Makerble}}{}
        {Ruby on Rails Developer}{March 2024 - Present}
      \resumeItemListStart
        \resumeItem{Collaborated with an android developer to integrate web app features into the mobile app by developing APIs, streamlining cross-platform interactions.}
        \resumeItem{Automated API workflows using scripts to update variables, significantly reducing manual work and accelerating development cycles.}
        \resumeItem{Facilitated the onboarding of new employees and mentored interns, ensuring a smooth transition into the team.}
        \resumeItem{Delivered business-critical features, such as event automation and question pool, enhancing overall user experience.}\resumeItem{Created clear documentation for processes, helping team members better understand workflows and boosting productivity.}
      \resumeItemListEnd
      
    % Makerble intern
    \resumeSubheadingConditional
      {}{}
      {Ruby on Rails Intern}{September 2023 - February 2024}
      \resumeItemListStart
        \resumeItem{Achieved a 40\% improvement in search performance through optimization of data retrieval functionalities.}
        \resumeItem{Enhanced data visualization capabilities on the survey analytics page by implementing filters for text-based questions, that provide users with deeper insights.}   
        \resumeItem{Improved the user interface by addressing navigation and alignment issues, resulting in a more intuitive experience and higher user satisfaction.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd
