
\section{{\textcolor{mainHeading}{Projects}}}
    \resumeSubHeadingListStart

    % Simple RSS
    \resumeProjectHeading
          {\textbf{Simple RSS} \ \
           \href{https://github.com/hokageCV/simple-rss}{{\footnotesize \faIcon{external-link-alt} }  } 
          }{}
          \resumeItemListStart
            \resumeItem{An RSS reader that aggregates updates from multiple feeds, allowing users to quickly view content and save time.}
            \resumeItem{Leveraged Gemini AI to summarize articles, making it easier for users to read key information.}
            \resumeItem{Supports export/import of feeds via OPML, offering users convenient management and backup.}
            \resumeItem{Built using \textit{Ruby on Rails, SQLite, Hotwire, Web Speech API}}
          \resumeItemListEnd   
          
    % Grudu list
    \resumeProjectHeading
          {\textbf{Grudu List} \ \
           \href{https://github.com/hokageCV/grudu-list}{{\footnotesize \faIcon{external-link-alt} }  } 
          }{}
          \resumeItemListStart
            \resumeItem{Developed the backend for group to-do list to effectively manage shared tasks.}
            \resumeItem{Implemented role-based access control to ensure secure task management within groups.}
            \resumeItem{Wrote tests using RSpec to verify functionality and maintain application stability.}
            \resumeItem{Built using \textit{Ruby on Rails, PostgreSQL, NextJS}}
          \resumeItemListEnd
          
    % Lakshya
      \resumeProjectHeading
         {\textbf{Lakshya} \ \ \href{https://github.com/hokageCV/Lakshya}
            { \footnotesize \faIcon{external-link-alt}    }   }{}
          \resumeItemListStart
            \resumeItem{A productivity extension that tracks the number of days that have passed in the year on a new tab.}
            \resumeItem{Encourages users to reflect on their time management by highlighting completed days.}
            \resumeItem{Built using \textit{Javascript, HTML, CSS, chrome API }}
          
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd
